pseudobulk_CMP

### 2021-09-13 pseudobulk_vs_bulk/pseudobulk_allPops.Rmd
Initiate new notebook to cycle through all 4 populations

@@

## Set global variables
```{r}
projectName <- "pseudobulk_CMP"
comparison_pop <- "CMP"
```

>>>>

## Update
### 2021.09.13
Finally got a method working for CMP vs. TotalSeq CMP (see pseudobulk_CMP.RMD). Will now clean up notebook and comparisons for both TotalSeq and ScriptSeq, and for all LSK, CMP, MEP, and GMP populations.

@@

## Set global variables
```{r}
projectName <- "pseudobulk_allPops"
comparison_pop <- "CMP"
```
